---
title: Reproduce supplementary figure
---

This is run in a separate script from the other figures due to issues with RStudio crashing when all scenarios were run from a single script.

If `run` is TRUE, it will run scenarios with double and triple the number of ECR patients.

To create the figure, it will use those files, as well as the baseline file created within `reproduction.qmd`.

Run time: 4.975 minutes (will vary between machines)

## Set up

```{r}
# Clear environment
rm(list=ls())

# Start timer
start.time <- Sys.time()

# Disable scientific notation
options(scipen=999)

# Get the model and helper functions (but hide loading warnings for each package)
suppressMessages(source("model.R"))
suppressMessages(source("helpers.R"))

# Import other required libraries (if not otherwise import in R scripts below)
library(ggpubr)
library(tidyr, include.only = c("pivot_wider"))
```

```{r}
# Set the seed and default dimensions for figures
SEED = 200
DEFAULT_WIDTH = 7
DEFAULT_HEIGHT = 4

# Set file paths to save results
folder = "../outputs"

path_baseline_f2 <- file.path(folder, "fig2_baseline.csv.gz")
path_double_sup <- file.path(folder, "sup_baseline_double.csv.gz")
path_triple_sup <- file.path(folder, "sup_baseline_triple.csv.gz")

path_supfig <- file.path(folder, "supplementary_figure.png")
```

## Run models

Set to true or false, depending on whether you want to run everything.

```{r}
run <- FALSE
```

Run baseline with double and triple the number of ECR patients, for the supplementary figure.

```{r}
if (isTRUE(run)) {
  baseline_sup2 <- run_model(seed = SEED, ecr_pt = 58*2)
  baseline_sup3 <- run_model(seed = SEED, ecr_pt = 58*3)
}
```
```{r}
if (isTRUE(run)) {
  # Save results
  data.table::fwrite(baseline_sup2, path_double_sup)
  data.table::fwrite(baseline_sup3, path_triple_sup)

  # Remove the dataframes from environment
  rm(baseline_sup2, baseline_sup3)
}
```

## Import results

Import the results, adding a column to each to indicate the scenario.

```{r import}
base_f2 <- import_results(path_baseline_f2, "Baseline")
base_sup_double <- import_results(path_double_sup, "Baseline (double)")
base_sup_triple <- import_results(path_triple_sup, "Baseline (triple)")
```

## Supplementary figure

```{r supplementary_figure}
# Create sub-plots
p1 <- create_plot(base_f2,
                  group="resource",
                  title="Baseline",
                  ylab="Standardised density of patient in queue")
p2 <- create_plot(base_sup_double,
                  group="resource",
                  title="Doubling ECR patients",
                  xlab="Patient wait time (min)",
                  xlim=c(0, 300),
                  breaks_width=100)
p3 <- create_plot(base_sup_triple,
                  group="resource",
                  title="Tripling ECR patients",
                  xlim=c(0, 300))

# Arrange in a single figure
ggarrange(p1, p2, p3, nrow=1,
          common.legend=TRUE, legend="bottom",
          labels=c("A", "B", "C"))
ggsave(path_supfig, width=DEFAULT_WIDTH, height=DEFAULT_HEIGHT)
```

## Time elapsed

```{r timer}
if (isTRUE(run)) {
  end.time <- Sys.time()
  elapsed.time <- round((end.time - start.time), 3)
  elapsed.time
}
```
