---
title: Reproduce Figures 2-4 and in-text results 1-3
---

The majority of the items in the model scope are reproduced in this file, but Figure 5 and the supplementary figure are created in seperate `.qmd` files.

This decision was primarily due to issues with RStudio crashing when running all scenarios from a single `.Rmd file`.

Run time: 18.024 minutes (will vary between machines)

## Set up

```{r}
# Clear environment
rm(list=ls())

# Start timer
start.time <- Sys.time()

# Disable scientific notation
options(scipen=999)

# Import required libraries (if not otherwise import in R scripts below)
library(ggpubr)
library(tidyr, include.only = c("pivot_wider"))

# Get the model and helper functions (but hide loading warnings for each package)
suppressMessages(source("model.R"))
suppressMessages(source("helpers.R"))
```

```{r}
# Set the seed and default dimensions for figures
SEED = 200
DEFAULT_WIDTH = 7
DEFAULT_HEIGHT = 4

# Set file paths to save results

folder = "../outputs"

path_baseline_f2 <- file.path(folder, "fig2_baseline.csv.gz")
path_exclusive_f2 <- file.path(folder, "fig2_exclusive.csv.gz")
path_twoangio_f2 <- file.path(folder, "fig2_twoangio.csv.gz")

path_baseline_f3 <- file.path(folder, "fig3_baseline.csv.gz")
path_exclusive_f3 <- file.path(folder, "fig3_exclusive.csv.gz")
path_twoangio_f3 <- file.path(folder, "fig3_twoangio.csv.gz")

path_txt2 <- file.path(folder, "txt2.csv") # Used for results 1 and 2
path_txt3 <- file.path(folder, "txt3.csv")
path_fig2 <- file.path(folder, "fig2.png")
path_fig3 <- file.path(folder, "fig3.png")
path_fig4 <- file.path(folder, "fig4.png")
```

## Run models

Set to true or false, depending on whether you want to run everything.

```{r}
run <- FALSE
```

Run model scenarios.

```{r}
if (isTRUE(run)) {
  # Run model
  baseline <- run_model(seed = SEED)
  baseline_6pm <- run_model(shifts = c(8,18), seed = SEED)
  baseline_7pm <- run_model(shifts = c(8,19), seed = SEED)

  exclusive <- run_model(exclusive_use = TRUE, seed = SEED)
  exclusive_6pm <- run_model(shifts = c(8,18), exclusive_use = TRUE, seed = SEED)
  exclusive_7pm <- run_model(shifts = c(8,19), exclusive_use = TRUE, seed = SEED)

  twoangio <- run_model(angio_inr = 2, angio_ir=0, seed = SEED)
  twoangio_6pm <- run_model(shifts = c(8,18), angio_inr = 2, angio_ir=0, seed = SEED)
  twoangio_7pm <- run_model(shifts = c(8,19), angio_inr = 2, angio_ir=0, seed = SEED)
}
```
```{r}
# (in seperate cell to above as otherwise seemed to crash)
if (isTRUE(run)) {
  # Save results for Figure 2
  data.table::fwrite(baseline, path_baseline_f2)
  data.table::fwrite(exclusive, path_exclusive_f2)
  data.table::fwrite(twoangio, path_twoangio_f2)

  # Process and save results for Figure 3
  process_f3_data(baseline, baseline_6pm, baseline_7pm, path_baseline_f3)
  process_f3_data(exclusive, exclusive_6pm, exclusive_7pm, path_exclusive_f3)
  process_f3_data(twoangio, twoangio_6pm, twoangio_7pm, path_twoangio_f3)

  # Remove the dataframes from environment
  rm(baseline, baseline_6pm, baseline_7pm,
     exclusive, exclusive_6pm, exclusive_7pm,
     twoangio, twoangio_6pm, twoangio_7pm)
}
```

## Import results

Import the results, adding a column to each to indicate the scenario.

```{r import}
base_f2 <- import_results(path_baseline_f2,
                          "Baseline")
exc_f2 <- import_results(path_exclusive_f2,
                         "Exclusive use")
two_f2 <- import_results(path_twoangio_f2,
                         "Two AngioINRs")

base_f3 <- import_results(path_baseline_f3,
                          "Baseline")
exc_f3 <- import_results(path_exclusive_f3,
                         "Exclusive use")
two_f3 <- import_results(path_twoangio_f3,
                         "Two AngioINRs")
```

## In-text results

In-text results 1 and 2

```{r in_text_1_and_2}
txt2 <- dplyr::bind_rows(base_f2, exc_f2, two_f2) %>%
  filter(resource=="angio_inr") %>%
  group_by(scenario) %>%
  summarize(mean = mean(wait_time)) %>%
  mutate(diff_from_baseline = round(mean - mean[1], 2))

# Save and display result
data.table::fwrite(txt2, path_txt2)
txt2
```

In-text result 3

```{r in_text_3}
txt3 <- dplyr::bind_rows(base_f3, exc_f3, two_f3) %>%
  filter(resource=="angio_inr") %>%
  group_by(scenario, shift) %>%
  summarize(mean = mean(wait_time)) %>%
  mutate(diff_from_5pm = round(mean - mean[1], 2))

# Save and display result
data.table::fwrite(txt3, path_txt3)
txt3
```

## Figure 2

```{r fig2}
# Create sub-plots
p1 <- create_plot(base_f2,
                  group="resource",
                  title="Baseline",
                  ylab="Standardised density of patient in queue")
p2 <- create_plot(exc_f2,
                  group="resource",
                  title="Exclusive-use",
                  xlab="Patient wait time (min)",
                  xlim=c(0, 250))
p3 <- create_plot(two_f2,
                  group="resource",
                  title="Double angio INRs")

# Arrange in a single figure
ggarrange(p1, p2, p3, nrow=1,
          common.legend=TRUE, legend="bottom",
          labels=c("A", "B", "C"))
ggsave(path_fig2, width=DEFAULT_WIDTH, height=DEFAULT_HEIGHT)
```

### Demonstrate that geom_density scaled is scaling against density of 0 wait time

```{r fig2_scaling}
# Create figure as usual
p <- create_plot(base_f2,
                 group="resource",
                 title="Baseline",
                 ylab="Standardised density of patient in queue")

# Get data from the plot
plot_data <- ggplot_build(p)$data[[1]]

# Create dataframe with the densities for when the waitimes are 0
no_wait <- plot_data %>% filter(x==0) %>% select(colour, density, scaled)

# Loop through each of the colours (which reflect the resource groups)
for (c in no_wait$colour) {
  # Filter the plot data to that resource group, then divide the densities by
  # the density from wait time 0
  d <- plot_data %>%
    filter(colour == c) %>%
    mutate(scaled2 = density / no_wait[no_wait$colour==c, "density"]) %>%
    ungroup() %>%
    select(scaled, scaled2)

  # Find the number of rows where these values match the scaled values
  n_match <- sum(apply(d, 1, function(x) length(unique(x)) == 1))
  n_total <- nrow(d)
  print(sprintf("%s out of %s results match", n_match, n_total))
}
```

## Figure 3

```{r fig3}
# Create sub-plots
p1 <- create_plot(base_f3,
                  group="shift",
                  title="Baseline",
                  ylab="Standardised density of patient in queue")
p2 <- create_plot(exc_f3,
                  group="shift",
                  title="Exclusive-use",
                  xlab="Patient wait time (min)",
                  xlim=c(0, 300),
                  breaks_width=100)
p3 <- create_plot(two_f3,
                  group="shift",
                  title="Double angio INRs",
                  xlim=c(0, 250))

# Arrange in a single figure
ggarrange(p1, p2, p3, nrow=1,
          common.legend=TRUE, legend="bottom",
          labels=c("A", "B", "C"))
ggsave(path_fig3, width=DEFAULT_WIDTH, height=DEFAULT_HEIGHT)
```

## Figure 4

```{r fig4}
# Get the relevant results from in-text results 1, 2 and 3
# Then calculate difference from baseline
fig4 <- dplyr::bind_rows(txt2 %>% select(scenario, mean),
                         txt3 %>%
                          filter(scenario=="Exclusive use", shift=="6pm") %>%
                          mutate(scenario="Exclusive use (+1h)") %>%
                          select(scenario, mean)) %>%
  mutate(diff = mean - mean[1]) %>%
  filter(scenario!="Baseline") %>%
  mutate(dis_free_gain = abs(diff)*4.2)

# Set order of the bars, and give full labels
fig4_col <- c("Exclusive use", "Two AngioINRs", "Exclusive use (+1h)")
fig4_col_l <- c("Exclusive-use", "Two angio INRs", "Exclusive-use and +1hr work")
fig4$scenario <- factor(fig4$scenario, levels=fig4_col)
fig4$scenario_lab <- plyr::mapvalues(fig4$scenario, from=fig4_col, to=fig4_col_l)

ggplot(fig4, aes(x=scenario_lab, y=dis_free_gain)) +
  geom_bar(stat="identity") +
  ylim(0, 32) +
  xlab("Scenarios") +
  ylab("Mean disability-free life added (days)")
ggsave(path_fig4, width=5, height=3)
```

## Time elapsed

```{r timer}
if (isTRUE(run)) {
  end.time <- Sys.time()
  elapsed.time <- round((end.time - start.time), 3)
  elapsed.time
}
```
